Seminarium TI 3700\\ Data Analysis on Twitter: An Overview

### 2014-03-26 paper_final.tex
Abstract 2.0

Twitter is a popular microblogging website that allows users to share 140 character messages (tweets) with the rest of the world.
The analysis of such messages has become its own field within information technology, with a range of techniques that all share the same cause:
extracting useful information from these messages. This paper serves as an introduction to the research that has been done analysing tweets from Twitter,
covering the API and a series of common techniques. One of the key factors that contribute to successful extraction is data enrichment, or somehow enhancing
the intended information from a tweet. This can be done by several techniques, yet this paper's scope limits to concept analysis and sentiment analysis.
When a stream of tweets is available for analysis, other techniques such as user classification, tag-based analysis and event identification offer valuable
insights into the behaviour of users on Twitter. All these techniques allow researchers to extract interesting information from Twitter activity, and allow
for a variety of applications to be created using this information.
\end{abstract}

@@

%TODO: Duidelijk zeggen dat het om een survey gaat, en een duidelijke werkmethodiek introduceren

>>>>

Twitter is a popular microblogging website that allows users to share 140 character messages (tweets) with the rest of the world.
The analysis of such messages has become its own field within information technology, with a range of techniques that all share the same cause:
extracting useful information from these messages. This paper serves as a survey to the research that has been done analysing tweets from Twitter,
covering the API and a series of common techniques. One of the key factors that contribute to successful extraction is Data Enrichment, or the enhancement
the intended information from a tweet. Another key factor is Sentiment Analysis, where an intended sentiment is recognized from the tweets.
When a stream of tweets is available for analysis, other techniques such as user classification, tag-based analysis and event identification offer valuable
insights into the behaviour of users on Twitter. The User Classification technique tries to divide a set of tweets over a set of proposed classes. 
The Tag Based Analysis uses the content in a tweet to link users with each other. It uses attachments such as hashtags, urls, images, other users, etc. to
create relations within a set of tweets. The final technique is Event Detection, where real time tweets are analysed to recognize real world events that
are happening at some given time. Before we conclude the techniques, we illustrate some useful applications that can be accomplished by applying the extracted
information. All these techniques allow researchers to extract interesting information from Twitter activity, and allow
for a variety of applications to be created using this information.
\end{abstract}

@@
